Compositional equivalences based on Open pNets

### 2020-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
corrected states in page 71

Figure \ref{Appendix:ImplOA} shows a more compact version of this weak automation, that will be easier to read for humans...
It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
In this configuration we can garanty that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure.
\TODO{May be express this property more formely, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}

@@

All following transitions are parametrized by an arbitrary non-negative integer $n\in \mathcal{N}$:

$ WI_3(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
$

$ WI_{3a}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n, \texttt{s2\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
$

$ WI_{3b}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s2\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
$

$ WI_{3c}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{r1\_msg}\gets \texttt{m}, \texttt{r1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 201}
$

@@

The next two  transitions show the same problem, as they include dependencies on $s1\_msg$:

\medskip
$ WI_7(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
         {100 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ WI_{7a}(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
         {210 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ WI_{7b}(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
         {220 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 1$

@@

         \subsection{Details of the Bisimulation Checking}
         \TODO{To be added}

>>>>

Figure \ref{Appendix:ImplOA} shows a more compact version of this weak automation, that will be easier to read for humans...
It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
In this configuration we can garanty that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this equivalence class of states as $\{000,202\}$.
\TODO{May be express this property more formely, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}

@@

All following transitions are parametrized by an arbitrary non-negative integer $n\in \mathcal{N}$.

$ WI_3(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
$

$ WI_{3a}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n, \texttt{s2\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
$

$ WI_{3b}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s2\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
$

$ WI_{3c}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{r1\_msg}\gets \texttt{m}, \texttt{r1\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 201}
$

@@

\medskip
$ WI_7(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
         {210 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$WI_{7a}$ shows the same problem, as it  includes a dependency on $s1\_msg$:

$ WI_{7a}(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
         {220 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ WI_{7b}(n) = \openrule
         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
         {100 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 1$

@@

         \subsection{\TODO{Details of the Bisimulation Checking}}
